Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-07-07 MUSES_vs_BYOD_solutions.tex
Adding clarification about MUSES advantages with respect to self-adaptation. Related to #35

Another comparison would be that the existing products are mostly policy-based, while MUSES makes its decisions not only considering policies, but also based on the terminals and users context. Thus it uses connection properties, or the device trust value, for instance, to really understand the real risk that comes with a specific action.

>>>>

Another comparison would be that the existing products are mostly policy-based, while MUSES makes its decisions not only considering policies, but also based on the terminals and users context (connection properties, or trust value of the device, for instance), to really understand the real risk that comes with a specific action.
